Analysis of Retrospective COVID-19 data

### 2020-11-26 dev/raw_data_preprocessing.Rmd
Working with the new dataset
Cleaning up, finishing touches on manuscript, work on supplement

TODO: check last day

@@

```{r}
complete_data$patient_data %>% group_by(hospital_id) %>%
  summarise(n())
```

>>>>

@@

```{r}
complete_data$patient_data %>% group_by(hospital_id) %>%
  summarise(n())
```
Data collection periods

```{r}
data_collection_period <- complete_data$patient_data %>% group_by(hospital_id) %>%
  summarise(first_admission = min(admission), last_admission = max(admission), .groups = "drop") %>%
  arrange(first_admission) %>%
  mutate(hospital_id_anon = 1:n()) %>% 
  select(-hospital_id)

write_csv(data_collection_period, here::here("manuscript", "data_collection_period.csv"))
```

```{r}
complete_data$patient_data <- complete_data$patient_data  %>% mutate(first_wave = admission < lubridate::ymd("2020-09-01"))
```

### 2020-11-26 manuscript/analysis_brms.Rmd
Cleaning up, finishing touches on manuscript, work on supplement

# {.tabset}

## Setup

@@

```{r}
#Marking the results as suspicious because there was a divergence...
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r, results="hide"}
form_survival_time <- bf(
  day | cens(censored) ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

@@

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time")
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")
```

```{r}
summary(fit_survival_time)
loo(fit_survival_time)
```

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "some influencial observations"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  )
)
```

>>>>

# Bayesian models with brms

@@

```{r}
#Marking the results as suspicious because there was a divergence...
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r, results="hide"}

@@

```

### Fewer adjustments

```{r}
form_survival_time_small <- bf(
  day | cens(censored) ~ sex + age_norm  + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

fit_survival_time_small <- brm(
  formula = form_survival_time_small,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time_small")
)
fit_survival_time_small <- add_criterion(fit_survival_time_small, "loo")

```

```{r}
summary(fit_survival_time_small)
loo(fit_survival_time_small)
```

```{r}
draws <- tidy_draws(fit_survival_time_small)
hypothesis_res_list[["hcq_az_survival_time_small"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm",
    model_check = "some influential observations"
  )
)
```

### Fewer adjustments - First wave only

```{r}

fit_survival_time_small_fw <- brm(
  formula = form_survival_time_small,
  data = data$surv_data_last_day %>% filter(first_wave),
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time_small_fw")
)
fit_survival_time_small_fw <- add_criterion(fit_survival_time_small_fw, "loo")

```

```{r}
summary(fit_survival_time_small_fw)
loo(fit_survival_time_small_fw)
```

```{r}
draws <- tidy_draws(fit_survival_time_small_fw)
hypothesis_res_list[["hcq_az_survival_time_small_fw"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, first_wave",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, first_wave",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, first_wave",
    model_check = "some influential observations"
  )
)
```

### More adjustments

```{r}
form_survival_time <- bf(
  day | cens(censored) ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

fit_survival_time <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day,
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time")
)
fit_survival_time <- add_criterion(fit_survival_time, "loo")

```

```{r}
summary(fit_survival_time)
loo(fit_survival_time)
```
There were some very influential observations.

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

### More adjustments - First wave only

```{r, results="hide"}
fit_survival_time_fw <- brm(
  formula = form_survival_time,
  data = data$surv_data_last_day %>% filter(first_wave),
  prior = prior_survival_time,
  inits = 0,
  control = default_control,
  file = paste0(cache_dir, "/fit_survival_time_fw")
)
fit_survival_time_fw <- add_criterion(fit_survival_time_fw, "loo")
```

```{r}
summary(fit_survival_time_fw)
loo(fit_survival_time_fw)
```

There were some very influential observations.

```{r}
draws <- tidy_draws(fit_survival_time_fw)
hypothesis_res_list[["hcq_az_survival_time_fw"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity, first_wave",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity, first_wave",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity, first_wave",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "log(OR)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

There were some very influential observations

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "some influential observations"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "some influential observations"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "Suspicious"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_hospital,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_hospital,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = -draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_hospital,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity",
    model_check = "probably overconfident"
  )
)
```

### Basic Categorical model (7 Days), first wave only

```{r, results="hide"}
fit_outcome_base_7_fw <- brm(
  formula = form_outcome_base,
  data = data$surv_data_7 %>% filter(first_wave),
  prior = prior_outcome_base,
  control = default_control,
  file = paste0(cache_dir, "/fit_outcome_base_7_fw")
)
fit_outcome_base_7_fw <- add_criterion(fit_outcome_base_7_fw, "loo")
```

```{r}
summary(fit_outcome_base_7_fw)
pp_check(fit_outcome_base_7_fw)
loo(fit_outcome_base_7_fw)
# ce <- conditional_effects(fit_outcome_base_7_fw)
# plot(ce, ask = FALSE)
```
